### 2016-01-18 papers/CAFe/HIPS-paper/coarray-extensions.tex
Added comment at end that perhaps could be used in final version regarding domain specific languages (for D-TEC purposes).

>>>>

\begin{comment}
It is noted that these extensions to Fortran have been described in terms
explicit language syntax modifying the base language.  CAFe could equivalently have
been described in terms of compiler directives.  For example, subimage task execution could be
written as
\begin{verbatim}
 call relax(U[device]) !$OFP [[device]]
\end{verbatim}
which would allow a standard CAF compiler to compile CAFe programs.  This gives
the flavor of a domain specific language.
\end{comment}
